Optical Music Recognition for MIDI-LilyPond File Generation

### 2024-05-07 papers/cs444/paper-cs444.tex
paper work

With the following conditions in mind, I propose an Image-to-MIDI model to serve a few purposes. First, this model will serve to convert image data to relative musical data to a high degree of accuracy. The process of converting MIDI to an image is trivial, but the opposite is a known Optical Music Recognition (OMR) problem in that the correlation is nonexistent. Second, a highly reliable model of this type will be capable of serving as an intermediate step in future audio computation endeavors, as the nontrivial nature of OMR is a barrier for reliable model training between scores and other types of audio data. Finally, a conversion of this type allows for more flexible datasets because MIDI can be converted into a number of other audio file types.

From a technical standpoint, my project will consist of: the construction of a trained model to relate images to MIDI data, a paper describing the process of constructing the model, and any notable results and accuracies, and a few demos from which the accuracy of the model can also be visually confirmed. The model will generally reference existing OMR research and will serve as an attempt to construct a completely new CNN model, (not be an implementation of an existing paper). Existing MIDI datasets have been narrowed down to strictly two-stave piano works by Johann Sebastian Bach to maintain rhythmic and compositional uniformity, although a generalized model for various instruments and number of staves can theoretically be produced given a large enough dataset.

Along with serving as my four-credit-hour project for the course, this model will serve as a supplementary step in my MS thesis- a separately-proposed model for generating audio conditioned on sheet music, advised by Paris Smaragdis. I can confirm that neither project will trivialize the other, and the flexibility of this project will open the door for other interesting ML-audio research in the future. For further results, I may pursue auto-transcription with this model to further differentiate from my planned thesis.

@@

>>>>

With the following conditions in mind, I propose an Image-to-MIDI model to serve a few purposes. First, this model serves to convert image data to relative musical data to a high degree of accuracy. The process of converting MIDI to an image is trivial, but the opposite is a known Optical Music Recognition (OMR) problem in that the correlation is nonexistent. 
Second, a highly reliable model of this type is capable of serving as an intermediate step in future audio computation endeavors, as the nontrivial nature of OMR is a barrier for reliable model training between scores and other types of audio data. 
Finally, a conversion of this type allows for more flexible datasets because MIDI can be converted into a number of other audio file types.

This model generally references existing OMR research and serves as an attempt to construct a completely new CNN model. Existing MIDI datasets have been narrowed down to strictly two-stave piano works by Johann Sebastian Bach to maintain rhythmic and compositional uniformity, although a generalized model for various instruments and number of staves can theoretically be produced given a large enough dataset.

@@

\subsection{Dynamic quantization}
\todo{quantization stuff}

\subsection{CRNN Model}
\todo{CRNN model}
